\documentclass[12pt]{exam}

\usepackage{amsmath,amsfonts, amsthm}
\newcommand{\ds}{\ensuremath{\displaystyle}}
\newcommand{\setB}[2]{\left\{#1:#2\right\}}

\printanswers

\begin{document}

\begin{center}
\fbox{\fbox{\parbox{5.5in}{\centering
MA437 - 2019 Spring - Sample Assessment - Dr. Clontz
}}}
\end{center}
\vspace{0.1in}
\makebox[\textwidth]{
  Name:\enspace\hrulefill\hrulefill\hrulefill\space
}

\vspace{12pt}

Circle the most appropriate response for each.

\section*{Module 1 Computation}

\begin{questions}

\setcounter{question}{0}

%\question Compute \((2,-3)(4,-2)\). 
%\begin{choices}
%\choice \(14\) 
%\choice \(-5 \)
%\choice \(-7 \)
%\choice None of these. 
%\end{choices}

\question Let \(z=4-3i\). Find \(z^{-1}\).
\begin{choices}
\choice \(\frac{4}{25}+\frac{3}{25}i\)
\choice \(-\frac{4}{25}+\frac{3}{25}i\)
\choice \(\frac{3}{25}-\frac{4}{25}i\)
\choice None of these. 
\end{choices}

\question Simpify \(\overline{\sqrt2 + 3i - i(5+i\sqrt2)}\). 
\begin{choices}
\choice \(-5\sqrt2 -3i\)
\choice \(7\sqrt2 -1-i\)
\choice \(2\sqrt2 +2i \)
\choice None of these. 
\end{choices}

\question Compute \(|5-12i|\)
\begin{choices}
\choice \(-7\)
\choice \(13\)
\choice \(17\)
\choice None of these. 
\end{choices}

\question Find the exponential form of \(\sqrt3-i\).
\begin{choices}
\choice \(2e^{-i\pi/6}\)
\choice \(3e^{-i\pi/3}\)
\choice \(4e^{i\pi/4}\)
\choice None of these. 
\end{choices}

\question Compute \((2-2\sqrt3 i)^{-3}\).
\begin{choices}
\choice \(\frac{1}{16}i\)
\choice \(\frac{1}{4}-\frac{1}{3}i\)
\choice \(-\frac{1}{64}\)
\choice None of these. 
\end{choices}
\end{questions}

\section*{Module 1 Knowledge}

\begin{questions}

\setcounter{question}{5}

\question The product \((0,1)(0,y)\) simplifies to \((-y,0)\).
\begin{choices}
\choice True
\choice False
\end{choices}

\question The additive inverse of \(x+yi\) is \(\frac{x}{x^2+y^2}-i\frac{y}{x^2+y^2}\).
\begin{choices}
\choice True
\choice False
\end{choices}

\question The graph of \(\setB{z}{|z+2-i|=3}\) is a parabola.
\begin{choices}
\choice True
\choice False
\end{choices}

\question \(|Re(z)|\leq|z|\) for all complex \(z\). 
\begin{choices}
\choice True
\choice False
\end{choices}

\question \(Arg(zw)=Arg(z)+Arg(w)\) for all nonzero complex \(z,w\). 
\begin{choices}
\choice True
\choice False
\end{choices}
\end{questions}

\section*{Module 1 Proofs}

Choose at most one of the following exercises to submit to the instructor.

\begin{questions}

\setcounter{question}{10}

\question The statement \(Im(z)=\frac{z+\overline{z}}{2i}\) is false. Fix the formula
  and prove that your fixed formula is true. 
\question Let \(w,z\) be nonzero complex numbers. Prove that the multiplicative inverse of
  \(wz\) is the product of the multiplicative inverse of \(w\) with the multiplicative
  inverse of \(z\).
\question Prove that for any value of \(arg(\frac{3}{z})\), there exists an equal value
  for \(-arg(z)\).

\end{questions}

\end{document}
