\documentclass[12pt]{article}

\usepackage[letterpaper,margin=1in]{geometry}

\setlength{\parindent}{0pt}

\usepackage{amssymb}
\usepackage{amsmath}

\usepackage{multicol}

\usepackage{tikz}

\newcommand{\headerText}{
  MA 237 | Spring 2018 | Dr. Clontz
}

\usepackage{fancyhdr}
\pagestyle{fancy}
\renewcommand{\headrulewidth}{0pt}% Default \headrulewidth is 0.4pt
\renewcommand{\footrulewidth}{0pt}% Default \footrulewidth is 0pt
\chead{\footnotesize\bf\headerText}
\cfoot{}

\newcommand{\csch}{\operatorname{csch}}
\newcommand{\sech}{\operatorname{sech}}

\newcommand{\issuesMark}{{\fontencoding{U}\fontfamily{futs}\selectfont\char 66\relax}}





\begin{document}


\begin{tikzpicture}[x=1in,y=1in]
  \draw[color=black!20] (0,0) rectangle (4.5,1);
  \draw[color=black!20] (0,0.67) -- (4.5,0.67);
  \draw[color=black!20] (3,0.33) -- (3,0.67);
  \draw[color=black!20] (0,0.33) -- (4.5,0.33);

  \node[anchor=west] at (0.1,0.83) {Name:};
  \node[anchor=west] at (0.1,0.5) {J\#:};
  \node[anchor=west] at (3.1,0.5) {Team:};
  \node[anchor=west] at (0.1,0.17) {Date:};

  \node at (5.5,0.5) {Office Form (\issuesMark{})};
\end{tikzpicture}

\vspace{1em}

\begin{tikzpicture}[x=1in,y=1in]
  \draw[color=black!50] (0,0) rectangle (6.4,1);
  \draw[color=black!50] (1,0) -- (1,1);
  \draw[color=black!50] (5.4,0) -- (5.4,1);

  \node[anchor=north west,color=black!70] at (0,0.95) {\footnotesize Standard:};
  \node[anchor=north west,text width=4.3in] at (1,0.95) {\textbf{Instructions:} Complete this form to be given the opportunity to
  attempt a new exercise for the designated standard during Wednesday
  office hours.};
  \node[anchor=north west,color=black!70] at (5.4,0.95) {\footnotesize Mark:};
\end{tikzpicture}


\renewcommand\labelitemi{\(\square\)}
Mark all that apply.
\begin{itemize}
  \item \textbf{I have attempted this standard before.}
        I received a mark of \issuesMark{} or better on a previous Mastery Quiz.
  \item \textbf{I am coming to class prepared.}
        I scored at least 70\% on the individual readiness assurance test (iRAT)
        for the most recent module, or I have reviewed all the
        readiness assurance resources for the module since the iRAT.
  \item \textbf{I have been participating in class.}
        I have been present and attentive in class for the last three
        class days,
        or my tardiness/absences have been for excusable reasons.
  \item \textbf{My team has been participating in class.}
        My team has satisfactorily participated in all class assignments
        for the past three class days, such as:
    \begin{itemize}
      \item any team readiness assurance tests
      \item activities completed on the whiteboard (not individual notes)
            and uploaded to Google Drive
    \end{itemize}
  \item \textbf{I have completed at least three homework exercises
        relevant to this standard, written on or attached to
        this form.}
        These exercises may be from any source, such as the textbook,
        internet, or old quizzes, as long as they demonstrate understanding
        of the relevant standard.
\end{itemize}

If you meet all these requirements,
bring this form to the instructor's \textbf{Wednesday office hours}.
If the attached exercises have been worked correctly, you will be given
a new exercise to complete, which will be marked immediately.
\textbf{If you
receive a \checkmark{}, you must wait a week before attempting this standard
again in office hours or on a quiz.}


\end{document}
